Draft-assinment1

### 2017-02-21 Draft-xuezhou-sjb.Rmd
findings

Through the process of summarizing these variables and analyzing the relationship between these variables, we found that for federally aided students in most colleges, around half (50.8%) of the students' parents did not complete the college.The average net price costs for most institutuins are falling into the range between $16000 - $20000. Among the 7703 institution samples, more than 50% of the students are able to receive Pell Grant or Federal Loans as means of finanical support??? and on average, 60% of students are financial independent. In most colleges, the students are able to reach the family income between $12000 and $18000.

>>>>

Through the process of summarizing these variables and analyzing the relationship between these variables, we found that for federally aided students in most colleges, around half of the students' parents did not complete the college.The average net price costs for most institutuins are falling into the range between $16000 - $20000. Among the 7703 institution samples, more than 50% of the students are able to receive Pell Grant or Federal Loans as means of finanical support, and on average, 60% of students are financial independent. In most colleges, the students are able to reach the family income between $12000 and $18000.
